\documentclass{resume}


\usepackage{times}

%% Use these lines for letter-sized paper

\iffalse
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

\setlength {\textheight} {9.00in}
\setlength {\columnsep} {0.33in}
\setlength {\textwidth} {7.0in}
\setlength {\topmargin} {-0.5in}
\setlength {\headheight} {0.0in}
\setlength {\headsep} {0.5in}
\setlength {\oddsidemargin} {-.25in}
\setlength {\parindent} {1pc}
\setlength {\baselineskip} {4in}
\fi

%\iffalse
% Use these lines for A4-sized paper
\usepackage[paper=a4paper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=30.5mm,    % Length of section titles
            marginparsep=1.5mm,       % Space between titles and text
            margin=25mm,              % 25mm margins
            includemp]{geometry}

\setlength {\textheight} {9.8in}
\setlength {\columnsep} {0.33in}
\setlength {\textwidth} {6.52in}
\setlength {\topmargin} {-0.5in}
\setlength {\headheight} {0.0in}
\setlength {\headsep} {0.5in}
\setlength {\oddsidemargin} {-.25in}
\setlength {\parindent} {1pc}
\setlength {\baselineskip} {4in}
%\fi




\newcommand{\myline}{\rule{0.90\textwidth}{0.5pt}}

\newcommand{\nolineskips}{
\setlength{\parskip}{1pt}
\setlength{\parsep}{1pt}
\setlength{\topsep}{1pt}
\setlength{\partopsep}{1pt}
\setlength{\itemsep}{1pt}}


\usepackage{revnum}

%\usepackage{thumbpdf}
\usepackage[pdftex,
        colorlinks=true,
        urlcolor=rltblue,       % \href{...}{...} external (URL)
        filecolor=rltgreen,     % \href{...} local file
        linkcolor=rltred,       % \ref{...} and \pageref{...}
        pdftitle={Koby Crammer},
        pdfauthor={Koby Crammer},
        pdfsubject={CV},
%        pdfkeywords={CV, resume},
        pdfproducer={pdfLaTeX},
%        pdfadjustspacing=1,
        pagebackref,
        pdfpagemode=UseOutlines,
        bookmarksopen=true]{hyperref}

\usepackage{color}
\definecolor{rltred}{rgb}{0.75,0,0}
\definecolor{rltgreen}{rgb}{0,0.5,0}
\definecolor{rltblue}{rgb}{0,0,1}
%\definecolor{rltblue}{rgb}{0.4,0.4,0.4}

\newcommand{\mysection}[1]{
\phantomsection\addcontentsline{toc}{section}{#1}\section*{\hspace{-0.5cm} #1}
}

\newcommand{\technion}{~Position at TECHNION~}
\newcommand{\upenn}{~Position at UPENN~}

\setbox1=\hbox{\technion}
\setbox2=\hbox{\upenn}




\author{Koby Crammer}%{\small November 6, 2009}}

\address{
Department of Electrical Enginering\\
The Technion\\
Technion City -  Haifa, 32000 \\
Israel\\
\href{mailto:koby@ee.technion.ac.il}{koby@ee.technion.ac.il}\\
}{+972-4-829-3274 (W)\\
+972-4-829-5757 (\,F\,)\\~\\~\\
\href{http://webee.technion.ac.il/people/koby/}{http://webee.technion.ac.il/people/koby/}
}


\begin{document}
\label{start}

\maketitle
\vspace{-4cm}
\centerline{Publications (updated March 29, 2015)}
\vspace{3.5cm}
\mysection{Publications}

Google Scholar PoP h-index 30 and g-index 84.
%Microsoft Academic Search h-index 21 and g-index 48. 


\subsection*{Book Chapters}
\begin{revnumerate}
\nolineskips

\item
{Koby Crammer}, From Binary Classification to Categorical Prediction.
In {\em Automatic Speech and Speaker Recognition: Large Margin and Kernel Methods}, Joseph Keshet
and Samy Bengio, Eds., John Wiley \& Sons, 2009.
\end{revnumerate}

\subsection*{Journals}
\begin{enumerate}
\nolineskips

\item
{Koby Crammer} and Yoram Singer.
\href{http://www.ai.mit.edu/projects/jmlr/papers/v2/crammer01a.html}
{On the Algorithmic Implementation of Multiclass Kernel-based Vector Machines}.
{\em Journal of Machine Learning Research} 2, 265-292, 2001.

\item
{Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/ecoc-mlj02.pdf}
{On the Learnability and Design of Output Codes for Multiclass Problems}.
{\em Machine Learning} 47, 201-233, 2002.

\item
{Koby Crammer} and Yoram Singer.
\href{http://www.ai.mit.edu/projects/jmlr/papers/v3/crammer03b.html}
{A Family of Online Algorithms for Category Ranking}.
 {\em Journal of Machine Learning Research} 3, 1025-1058, 2003.

\item
{Koby Crammer} and Yoram Singer.
\href{http://www.ai.mit.edu/projects/jmlr/papers/v3/crammer03a.html}
{Ultraconservative Online Algorithms for Multiclass Problems}.
 {\em Journal of Machine Learning Research} 3, 951-991, 2003.

\item
{Koby Crammer} and Yoram Singer
\href{http://www.mitpressjournals.org/doi/pdf/10.1162/0899766052530848}
{Online Ranking by Projecting}.
{\em Neural Computation} 17(1), 145 - 175, January 2005.
\\~\\\centerline{\hrulefill\raisebox{-0.5\ht2}{\upenn}\hrulefill}\\

\item
{Koby Crammer}, Ofer Dekel, Joseph Keshet, Shai Shalev-Shwartz and Yoram Singer.
\href{http://jmlr.csail.mit.edu/papers/v7/crammer06a.html}
{Online Passive-Aggressive Algorithms}.
 {\em Journal of Machine Learning Research} 7, 551-585, 2006.



\item
Axel Bernal, {Koby Crammer}, A. Hatzigeorgiou, and Fernando Pereira.
\href{http://compbiol.plosjournals.org/perlserv/?request=get-document&doi=10.1371/journal.pcbi.0030054}
{Global Discriminative Learning for Higher-Accuracy Computational Gene Prediction}.
{\em PLoS Computational Biology} 3, March 2007.

\item
{Koby Crammer}, Michael Kearns, and Jennifer Wortman.
\href{http://jmlr.csail.mit.edu/papers/v9/crammer08a.html}
{Learning from Multiple Related Data Sources}.  {\em Journal of Machine
Learning Research} 9, 1757--1774, 2008.

\item
Qian Liu, {Koby Crammer}, Fernando Pereira, and David S. Roos.
\href{http://www.biomedcentral.com/1471-2105/9/433}
{Reranking Candidate Gene Models with Cross-Species Comparison for Improved Gene Prediction}.  {\em BMC Bioinformatics} 9:433, 2008.
\\~\\\centerline{\hrulefill\raisebox{-0.5\ht1}{\technion}\hrulefill}\\

\item
Shai Ben-David, John Blitzer, {Koby Crammer}, Alex Kulesza, Fernando Pereira and Jennifer Wortman.
\href{http://www.springerlink.com/content/q6qk230685577n52/}{A Theory of Learning from Different Domains}.
{\em Machine Learning Journal}, Volume 79, Issue 1-2, May 2010.

\item
Mark Dredze, Alex Kulesza and {Koby Crammer}.
\href{http://www.springerlink.com/content/a78049767680386l/}{Multi-Domain Learning by Confidence-Weighted Parameter Combination} .
{\em Machine Learning Journal}, Volume 79 Issue 1-2, May 2010.

\item
Axel Bernal, Koby Crammer and Fernando Pereira.
\href{http://bioinformatics.oxfordjournals.org/content/early/2012/04/17/bioinformatics.bts176.full.pdf+html}{Automated Gene-Model Curation using Global Discriminative Learning}.
{\em Bioinformatics}, April 2012

\item
{Koby Crammer}, Mark Dredze and Fernando Pereira.
Confidence-Weighted Linear Classification for Natural Language
Processing.
{\em JMLR} 13(Jun):1891--1926, 2012. 

\item
Zhuang Wang, {Koby Crammer}, and Slobodan Vucetic.
Breaking the Curse of Kernelization: Budgeted Stochastic Gradient
Descent for Large-Scale SVM Training.
{\em JMLR} 13(Oct):3103-3131, 2012.


\item
{Koby Crammer} and Claudio Gentile.
\href{http://www.springer.com/home?SGWID=0-0-1003-0-0&aqId=2406203&download=1&checkval=951b947939b069f46cb63e1f6ee72695}{Multiclass Classification with Bandit Feedback using Adaptive
Regularization.}
{\em Machine Learning Journal},  Volume 90, Issue 3 (2013), Pages 347-383.


\item
{Koby Crammer}, Alex Kulesza and Mark Dredze.
\href{http://www.springer.com/alert/urltracking.do?id=Lffdd03Mc0e861Sb052601}{Adaptive Regularization of Weights}. 
{\em Machine Learning  Journal}, Volume 91, Issue 2 (2013), Pages 155-187.


\item Edward Moroshko and {Koby Crammer}.
\href{http://www.sciencedirect.com/science/article/pii/S0304397514007063}{Weighted Last-Step Min-Max Algorithm with Improved
  Sub-Logarithmic Regret}.
{\em TCS (Theoretical Computer Science)}, Volume 558 (2014), Pages 107-124.
\end{enumerate}



\subsection*{Journal Papers Accepted for Publication}
\begin{enumerate}
\nolineskips

% \item Hadas Benisty, David Malah, and {Koby Crammer}.
% Unaligned Voice Conversion Using Grid-Based Approximation.
% Submitted to {\em IEEE Transactions on audio, speech and language processing}.

\item Francesco Orabona, Koby Crammer and Nicolo Cesa-Bianchi. 
 A Generalized Online Mirror Descent with Applications to
   Classification and Regression.
{\em Machine Learning Journal}, to appear.

\item Koby Crammer, Edward Moroshko and Nina Vaits.
Second-Order Non-Stationary Online Learning for Regression.
{\em Journal of Machine Learning Research}, to appear.

\end{enumerate}



\subsection*{Submitted Journal Papers}
\begin{enumerate}
\nolineskips
% \item Hadas Benisty, David Malah, and {Koby Crammer}.
% Unaligned Voice Conversion Using Grid-Based Approximation.
% Submitted to {\em IEEE Transactions on audio, speech and language processing}.


%% \item Nina Vaitz, Edward Moroshko and {Koby Crammer}.
%% Second-Order Non-Stationary
%%   Online Learning for Regression. 
%% Submitted to {\em IEEE Transactions on Information Theory}.


\item Matan Orbach and Koby Crammer.
TACO: Transduction Algorithm with Confidence.
Submitted to {\em Machine Learning Journal}.



\end{enumerate}


\subsection*{Refereed Conference Papers}
\begin{enumerate}
\nolineskips


% \item A Simple Geometric Interpretation of SVM using Stochastic Adversaries
% In {\em Proceedings of the Fifteenth International Conference on
%   Artificial Intelligence and Statistics}, 2012 (to appear).

\item
{Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/colt00.pdf}{On the Learnability and Design of Output Codes for Multiclass Problems}.
In {\em Proceedings of the Thirteen Annual Conference on Computational Learning Theory}, 2000.

\item
{Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/nips00.pdf}{Improved Output Coding for Classification Using Continuous Relaxation}.
In {\em Proceedings of the Thirteen Annual Conference on Neural Information Processing Systems}, 2000.
\item
{Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/colt01.ps}{Ultraconservative Online Algorithms for Multiclass Problems}.
In {\em Proceedings of the  Fourteenth Annual Conference on Computational Learning Theory}, 2001.
\item
{Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/nips01.ps}{Pranking with Ranking}.
In {\em Proceedings of the Fourteenth Annual Conference on Neural Information Processing Systems}, 2001.
\item
{Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/sigir02.ps}{A New Family of Online Algorithms for Category Ranking}.
In {\em Proceedings of the 25rd Conference on Research and Development in Information Retrieval} (SIGIR),
2002.
\item
{Koby Crammer}, Ran Gilad-Bachrach, Amir Navot and Naftali Tishby.
\href{http://www.cis.upenn.edu/~crammer/publications/nips02b.pdf}{Margin Analysis of the LVQ Algorithm}.
In {\em Proceedings of the Fifteenth Annual Conference on Neural Information Processing Systems} (NIPS),
2002.
\item
{Koby Crammer}, Joseph Keshet and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/nips02a.pdf}{Kernel Design using Boosting}.
In {\em Proceedings of the Fifteenth Annual Conference on Neural Information Processing Systems} (NIPS),
2002.
\item
{Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/colt03.ps}{Learning Algorithms for Enclosing Points in Bregmanian Balls}.
In {\em Proceedings of the Fifteenth Annual Conference on Computational Learning Theory} (COLT), 2003.
\item {Koby Crammer}, Jaz Kandola and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/budget-nips03.pdf}{Online Classification on a Budget}.
In {\em Proceedings of the Sixteenth Annual Conference on Neural Information Processing Systems} (NIPS), 2003.
\item {Koby Crammer}, Ofer Dekel, Shai Shalev-Shwartz and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/passiveAggressive-nips03b.pdf}{Online Passive-Aggressive Algorithms}.
In {\em Proceedings of the Sixteenth Annual Conference on Neural Information Processing Systems} (NIPS), 2003.
\item
{Koby Crammer} and Gal Chechik.
\href{http://www.cis.upenn.edu/~crammer/publications/ocibn-icml04.pdf}{A Needle in a Haystack: Local One-Class Optimization}.
In {\em Proceedings of the Twenty-First International Conference on
  Machine Learning} (ICML), 2004.

\item Lavi Shpigelman, {Koby Crammer}, Rony Paz, Eilon Vaadia and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/ddt-nips04.pdf}{A Temporal Kernel-Based Model for Tracking Hand-Movements from Neural Activities}.
In {\em Proceedings of the Seventeenth Annual Conference on Neural Information Processing Systems} (NIPS), 2004.
\\~\\\centerline{\hrulefill\raisebox{-0.5\ht2}{\upenn}\hrulefill}\\

\item {Koby Crammer} and Yoram Singer.
\href{http://www.cis.upenn.edu/~crammer/publications/colt05.pdf}{Loss Bounds for Online Category Ranking}.
In {\em Proceedings of the Eighteenth Annual Conference on Computational Learning Theory} (COLT) , 2005.

\item Ryan McDonald, {Koby Crammer} and Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/dependencyACL2005.pdf}{Online Large-Margin Training of Dependency Parsers}.
In {\em Proceedings of the 43rd Annual Meeting of the Association for Computational Linguistics}, (ACL) 2005.

\item Ryan McDonald, {Koby Crammer} and Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/segmentationHLT-EMNLP2005.pdf}{Flexible Text Segmentation with Structured Multilabel Classification}.
In {\em Processing of Human Language Technology Conference on Empirical Methods in Natural Language Processing}, 2005.

\item
{Koby Crammer}, Michael Kearns, Jennifer Wortman
\href{http://www.cis.upenn.edu/~crammer/publications/vardata.pdf}{Learning from Data of Variable Quality}.
In {\em Proceedings of the Eighteenth Annual Conference on Neural Information Processing Systems (NIPS)}, 2005.
\item
{Koby Crammer} and Daniel D. Lee.
\href{http://www.cis.upenn.edu/~crammer/publications/icassp06.pdf}{Room Impulse Response Estimation Using Sparse Online Prediction and
Absolute Loss}.
In {\em Proceedings of the IEEE International conference on Acoustics, Speech and Signal Processing}, 2006.
\item {Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/colt06.pdf}{Online Tracking of Linear Subspaces}.
In {\em Proceedings of the 19th Annual Conference on Learning Theory},
438-452, 2006.
\item
{Koby Crammer} and Amir Globerson.
\href{http://www.cis.upenn.edu/~crammer/publications/qclass.pdf}{Discriminative Learning via Semidefinite Probabilities}.
In {\em proceedings of Uncertainty in Artificial Intelligence} (UAI), 2006
\item
  Linli Xu, {Koby Crammer}, Dale Schuurmans.
\href{http://www.cis.upenn.edu/~crammer/publications/AAAI0613XuL.pdf}{Robust Support Vector
  Machine Training via Convex Outlier Ablation}.
In {\em Proceedings of the Twenty-First National Conference on
  Artificial Intelligence}, 2006.
\item
Shai Ben-David, John Blitzer, {Koby Crammer}, and Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/nips06.pdf}{Analysis of Representations for Domain Adaptation}.
In {\em Advances in Neural Information Processing Systems 19}, 2006.
\item
{Koby Crammer}, Michael Kearns, and Jennifer Wortman.
\href{http://www.cis.upenn.edu/~crammer/publications/multisource_nips07.pdf}{Learning from Multiple Sources}.
In {\em Advances in Neural Information Processing Systems 19}, 2006.
\item
{Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/is2007.pdf}{A Conservative Aggressive Subspace Tracker}.
In {\em Proceedings of the 10th European Conference on Speech
  Communication and Technology} (Interspeech), 2007.
\item
John Blitzer, {Koby Crammer}, Alex Kulesza, Fernando Pereira and
  Jennifer Wortman.
\href{http://www.cis.upenn.edu/~crammer/publications/adaptation_weighting.pdf}
{Learning Bounds for Domain Adaptation}.
In {\em Advances in Neural Information Processing Systems 20}, 2007.
\item
Mark Dredze, {Koby Crammer} and Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/icml08_variance.pdf}{Confidence-Weighted Linear Classification}.
In {\em International Conference on Machine Learning 25}, 2008.
\item
{Koby Crammer}, Partha Pratim Talukdar and Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/icml08_ocrd.pdf}{A Rate-Distortion One-Class Model and its Applications to
  Clustering}.
In {\em International Conference on Machine Learning 25}, 2008.
\item
Mark Dredze and {Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/acl08_active_conf.pdf}{Active Learning with Confidence}.
In {\em Association for Computational Linguistics}, 2008.
\item
Partha Pratim Talukdar, Marie Jacob, Mohammad Salman Mehmood, {Koby Crammer}, Zack Ives, Fernando Pereira and Sudipto Guha.
\href{http://www.cis.upenn.edu/~crammer/publications/vldb08_kbdi.pdf}{Learning to Create Data-Integrating Queries}.
In {\em Proceedings of the 34th International Conference on Very Large Databases}, VLDB 2008.
\item
Ron Bekkerman and {Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/multi_domain_emnlp08.pdf}{One-Class Clustering in the Text Domain}.
In {\em Conference on Empirical Methods in Natural Language Processing}, 2008 .
\item
Mark Dredze and {Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/oc_emnlp08.pdf}{Online Methods for Multi-Domain Learning and Adaptation}.
In {\em Conference on Empirical Methods in Natural Language Processing}, 2008.
\item
{Koby Crammer}, Mark Dredze, Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/paper_nips08_std.pdf}{Exact Convex Confidence-Weighted Learning}.
In {\em Advances in Neural Information Processing Systems}, 2008.
\item
{Koby Crammer}, Mehryar Mohri, Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/gmms.pdf}{Gaussian Margin Machines}.
In {\em The proceedings of the twelfth International Conference on
Artificial Intelligence and Statistics}, 2009.
\item
Hui Lin, Jeff Bilmes and {Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/lp_is09.pdf}{How to Loose Confidence: Probabilistic Linear Machines for Multiclass Classification}.
In {\em Conference of the International Speech Communication Association (Interspeech)}, 2009.

\item
Partha Pratim Talukdar and {Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/adsorption_ecml09.pdf}{New Regularized Algorithms for Transductive Learning}.
In {\em European Conference on Machine Learning (ECML-PKDD)}, 2009.
\item
{Koby Crammer}, Mark Dredze and Alex Kulesza.
\href{http://www.cis.upenn.edu/~crammer/publications/mccw_emnlp09.pdf}{Multi-Class Confidence Weighted Algorithms}.
In {\em Empirical Methods in Natural Language Processing (EMNLP)},
2009.
\\~\\\centerline{\hrulefill\raisebox{-0.5\ht1}{\technion}\hrulefill}\\

\item
{Koby Crammer}, Alex Kulesza and Mark Dredze.
\href{http://webee.technion.ac.il/people/koby/publications/arow_nips09.pdf}{Adaptive Regularization Of Weight Vectors}.
In {\em Advances in Neural Information Processing Systems}, 2009.
\item
Ted Sandler, {Koby Crammer} and Lyle H. Ungar.
\href{http://webee.technion.ac.il/people/koby/publications/icdm2009_PID1023443.pdf}{Resolving Identity Uncertainty with Learned Random Walks}.
{\em IEEE International Conference on Data Mining}, 2009.

\item {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/icassp10.pdf}{Efficient online learning with individual learning-rates for Phoneme Sequence recognition}.
{\em The 35th International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}, 2010.

\item Justin Ma, Alex Kulesza, Mark Dredze, {Koby Crammer}, Lawrence K. Saul, and Fernando Pereira.
\href{http://webee.technion.ac.il/people/koby/publications/covariance-aistats2010.pdf}{Exploiting Feature Covariance in High-Dimensional Online Learning}.
{\em Proceedings of the International Conference on Artificial Intelligence and Statistics (AISTATS)}, 2010 .


\item
Zhuang Wang, Koby Crammer, Slobodan Vucetic.
\href{http://webee.technion.ac.il/people/koby/publications/ICML10_BPegasos.pdf}{Multi-Class Pegasos on a Budget}.
{\em Proceedings International Conference on Machine Learning (ICML)}, 2010, 1143-1150.

\item {Koby Crammer}, Eyal Even-Dar, Yishay Mansour, and Jennifer Wortman Vaughan.
\href{http://webee.technion.ac.il/people/koby/publications/conceptdrift.pdf}{Regret Minimization with Concept Drift}.
{\em Proceedings of the the 23rd Annual Conference on Learning Theory
  (COLT)}, 2010, 168-180.




\item Paramveer Dhillon, Partha Pratim Talukdar,and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/}{Learning Better Data Representation using Inference-Driven Metric Learning}.
{\em Proceedings of the Annual Meeting of the Association for Computational Linguistics}, 2010.

\item Avihai Mejer and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/paper_seq_emnlp10.pdf}{Confidence in Structured-Prediction using Confidence-Weighted Models}.
{\em Proceedings of the Conference on Empirical Methods in Natural
  Language Processing}, 2010, 971-981.

\item Francesco Orabona and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/adaptive_nips10.pdf}{New Adaptive Algorithms for Online Classification}.
{\em Proceedings of the Annual Conference on Neural Information
  Processing Systems (NIPS)}, 2010, 1840-1848.

\item  {Koby Crammer} and Daniel D. Lee.
\href{http://webee.technion.ac.il/people/koby/publications/gaussian_mob_nips10.pdf}{Learning via Gaussian Herding }.
{\em Proceedings of the Annual Conference on Neural Information Processing
  Systems  (NIPS)}, 2010, 451-459.

\item Zhuang Wang, Nemanja Djuric, Koby Crammer, Slobodan Vucetic.
\href{http://webee.technion.ac.il/people/koby/publications/KDD2011.pdf}{Trading Representability for Scalability: Adaptive Multi-Hyperplane Machine for Nonlinear Classification}.
{\em ACM SIGKDD Int. Conf. on Knowledge Discovery and Data Mining
  (KDD)}, 2011, 24-32.

\item Noam Slonim, Elad Yom-Tov, Koby Crammer.
\href{http://webee.technion.ac.il/people/koby/publications/2011_4_14_scy_ijcai_final.pdf}{Active online classification via information maximization}.
{\em Proceedings of the 22nd International Joint Conference on
  Artificial Intelligence (IJCAI)}, 2011, 1498-1504.

\item Koby Crammer, Claudio Gentile.
\href{http://webee.technion.ac.il/people/koby/publications/mcbandit_icml11.pdf}{Multiclass classification with bandit feedback using adaptive regularization}.
{\em Proc. of the 26th International Conference on Machine Learning
  (ICML)}, 2011, 273-280.

\item Nina Vaits, Koby Crammer.
\href{http://webee.technion.ac.il/people/koby/publications/ada_arow_alt2011.pdf}{Re-Adapting the Regularization of Weights for Non-Stationary
  Regression}.
{\em Proc. of the 22nd International Conference on Algorithmic Learning Theory
(ALT)}, 2011, 114-128.

\item Roi Livni, {Koby Crammer} and Amir Globerson.
\href{http://webee.technion.ac.il/people/koby/publications/229_paper.pdf}{A Simple Geometric Interpretation of SVM using Stochastic Adversaries}.
{\em Proceedings of the 15th International Conference on Artificial Intelligence and Statistics (AISTATS)}, 2012.

\item {Koby Crammer}, Alex Kulesza and Mark Dredze.
\href{http://webee.technion.ac.il/people/koby/publications/icassp12_rls.pdf}{New
  $H_\infty$ Bounds for the Recursive Least Squares Algorithm Exploiting Input Structure}.
{\em The 37th International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}, 2012.
 

\item {Koby Crammer} and Daniel.D. Lee.
\href{http://webee.technion.ac.il/people/koby/publications/icassp12_nherd.pdf}{Online
  Discriminative Learning of Phoneme Recognition via Collections of Generalized Linear Models}.
{\em The 37th International Conference on Acoustics, Speech, and Signal Processing (ICASSP)}, 2012.
 
\item Avihai Mejer and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/conf_parsing_naacl12.pdf}{Are You Sure? Confidence in Prediction of Dependency
          Tree Edges}.
{\em Conference of the North American Chapter of the Association for
  Computational Linguistics: Human Language Technologies}, 2012.

 
\item Avihai Mejer and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/light_naacl12.pdf}{Training Dependency Parser Using Light Feedback}.
{\em Conference of the North American Chapter of the Association for
  Computational Linguistics: Human Language Technologies}, 2012.


\item 
 {Koby Crammer} and Gal Chechik.
\href{http://webee.technion.ac.il/people/koby/publications/icml12_aroma.pdf}{Adaptive Regularization for Similarity Measures}.
{\em ICML}, 2012.


\item 
Hadas Benisty, David Malah and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/1569582663.pdf}{Modular Global Variance Enhancement for Voice Conversion Systems}.
{\em EUSIPCO}, 2012.



\item 
Matan Orbach and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/ecml12taco.pdf}{Graph Based Transduction with Confidence}.
{\em ECML-PKDD}, 2012.


\item

Edward Moroshko and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/alt12.pdf}{Weighted Last-Step Min-Max Algorithm with Improved Sub-Logarithmic Regret}.
{\em ALT}, 2012.

\item Koby Crammer and {Tal Wagner}.
\href{}{Volume Regularization for Binary Classification}.
{\em NIPS}, 2012.


\item Koby Crammer and {Yishay Mansour}.
\href{}{Learning Multiple Tasks using Shared Hypotheses}.
{\em NIPS}, 2012.

\item Yoav Haimovitch, {Koby Crammer} and Shie Mannor.
\href{http://webee.technion.ac.il/people/koby/publications/haimovitch124.pdf}{More Is Better: Large Scale Partially-supervised Sentiment Classification}
{\em ACML}, 2012.

\item Matan Orbach and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/taco_ieeei12.pdf}{Transductive Phoneme Classification Using Local Scaling And Confidence}.
{\em IEEE 27-th Convention of Electrical and Electronics
  Engineers in Israel (IEEEI)}, 2012

\item Paramveer S. Dhillon, Partha Pratim Talukdar and {Koby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/graph_da_coling_2012}{Metric Learning for Graph-based Domain Adaptation}.
{\em The 24th International Conference on Computational Linguistics (COLING)}, 2012.


\item Edward Moroshko and {Koby Crammer}.
\href{}{A Last-Step Regression Algorithm for Non-Stationary Online Learning}.
{\em AISTATS}, 2013.


\item Noam Slonim, Ehud Aharoni and, {Koby Crammer}.
\href{}{Hartigan's $K$-means vs. Lloyd's $K$-means -- is it time for a change?}
{\em IJCAI}, 2013.

\item  
Ben Zion Vatashsky and {Koby Crammer}.
\href{}{Multi Class Learning with Individual Sparsity}.
{\em IJCAI}, 2013.

\item Yevgeny  Seldin , Peter  Bartlett , Koby  Crammer and, Yasin  Abbasi-Yadkori
\href{}{Prediction with Limited Advice and Multiarmed Bandits with Paid Observations}.
{\em ICML}, 2014.

\item Edward Moroshko and {Koby Crammer}.
\href{}{Selective Sampling with Drift }.
{\em AISTATS}, 2014.

\item Asaf Noy and {Koby  Crammer}.
\href{}{Robust Forward Algorithms via PAC-Bayes and Laplace Distributions}.
{\em AISTATS}, 2014.

\item {Koby  Crammer}.
\href{}{Doubly Aggressive Selective Sampling Algorithms for Classification}.
{\em AISTATS}, 2014.

\item Hadas Benisty, David Malah, and {Koby Crammer}
\href{}{Non-Parallel Voice Conversion Using Joint Optimization of Alignment 
by Temporal Context and Spectral Distortion}. 
{\em ICASSP}, 2014.

\item Maayan Harel, Shie Mannor, Ran El-Yaniv and, {Koby Crammer}. 
\href{}{Concept Drift Detection Through Resampling}.
{\em ICML}, 2014.

\item Tor Lattimore, {Koby Crammer} and Csaba Szepesvari.
\href{}{Optimal Resource Allocation with Semi-Bandit Feedback}.
{\em UAI}, 2014. {\em Best Paper Runner-up Award}.

\item Haim Cohen and {Koby Crammer}.
 \href{}{Learning Multiple Tasks in Parallel with a Shared
   Annotator}. 
{\em NIPS} 2014.


\item Hadas Benisty and {Koby Crammer}.
\href{}{Metric Learning Using Labeled and Unlabeled Data for Semi-Supervised/Domain
Adaptation Classification}.
{\em IEEE 28-th Convention of Electrical and Electronics
  Engineers in Israel (IEEEI)}, 2014.


\item Hadas Benisty, David Malah and {Koby Crammer}.
\href{}{Sequential Voice Conversion Using Grid-Based Approximation}.
{\em IEEE 28-th Convention of Electrical and Electronics
  Engineers in Israel (IEEEI)}, 2014.


\item Itamar Katz and {Koby Crammer}.
 \href{}{Outlier-Robust Convex Segmentation}. 
{\em AAAI} 2015, to appear.


\item Aviad Barzilay and {Koby Crammer}.
\href{}{Convex Multi-Task Learning by Clustering}. 
{\em AISTATS} 2015, to appear.


\end{enumerate}

\iffalse
\subsection*{Submitted Conference Papers}
\begin{revnumerate}

\item
{Koby Crammer}, and Daniel D. Lee.
Learning via Gaussian Herding.

\item
Francesco Orabona and {Koby Crammer}.
New Adaptive Algorithms for Online Classification.

\item
Avihai Mejer and {Koby Crammer}.
Confidence in Structured-Prediction using Confidence-Weighted Linear Models.

\item
Noam Slonim, Elad Yom-Tov and {Koby Crammer}.
Information based classifier for online text classification.
\end{revnumerate}
\fi

%\newpage
\subsection*{Workshop Papers, Abstracts and Technical Reports}
\begin{enumerate}
\nolineskips
\item {Koby Crammer} and Yoram Singer.
A Family of Online Algorithms for Category Ranking.
{\em NIPS 2002 workshop: Beyond Classification and Regression; Learning Rankings,
    Preferences, Equality Predicates, and Other Structures}, 2002.

\item {Koby Crammer} and Yoram Singer.
An Apparatus for General Discriminative Categorization with Kernel Machines.
A Poster. Presented at the {\em Sixteenth Annual Conference on Computational Learning Theory} (COLT) , 2003.

\item {Koby Crammer} and Noam Slonim.
The Information-Bottleneck and data-representation : Bregman to the rescue.
{\em NIPS 2003 workshop: Information Theory and Learning; The Bottleneck and Distortion Approach}.

\item {Koby Crammer} and Yoram Singer.
Online Topic Ranking for Text Documents.
A demonstration at the
{\em Sixteenth Annual Conference on Neural Information Processing Systems} (NIPS), 2003.

\item {Koby Crammer}.
\href{http://www.cis.upenn.edu/~crammer/publications/thesis.pdf}
{Online Learning of Complex Categorical Problems}.
PhD Thesis, Hebrew University, 2004.

\item Ryan McDonald, {Koby Crammer} and Fernando Pereira.
Large Margin Online Learning Algorithms for Structured Classification.
{\em NIPS 2004 workshop: Learning With Structured Outputs Workshop}.

\item {Koby Crammer}, Ryan McDonald, and Fernando Pereira.
New Large Margin Algorithms for Structured Prediction.
{\em NIPS 2004 workshop: Learning With Structured Outputs Workshop}.

\item {Koby Crammer}, Ryan McDonald  and Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/scalable.pdf}{Scalable Large-Margin Online Learning for Structured Classification}
{\em Technical Report. Department of Computer and Information Science, University of Pennsylvania}, 2005.

\item
Kuzman Ganchev, {Koby Crammer},
Fernando Pereira, Gideon Mann, Kedar Bellare, Andrew McCallum, Steven
Carroll, Yang Jin, and Peter White.
\href{http://www.cis.upenn.edu/~crammer/publications/biocreativeII07.pdf}{Penn/UMass/CHOP BiocreativeII Systems}.
In {\em Proceedings of the Biocreative II  Workshop} p. 119 - 124, 2007.

\item
{Koby Crammer}, Mark Dredze, Kuzman Ganchev, Partha Pratim
  Talukdar and Steven Carroll.
\href{http://www.cis.upenn.edu/~crammer/publications/cmc_bionlp07.pdf}{Automatic Code Assignment to Medical Text}.
BioNLP 2007.
\item
Partha Pratim Talukdar, John Blitzer, Ted Sandler, Mark Dredze, {Koby Crammer} and Fernando Pereira.
\href{http://www.cis.upenn.edu/~crammer/publications/icml08_draso.pdf}{DRASO: Declaratively Regularized Alternating Structural Optimization}.
ICML 2008 Workshop on Prior Knowledge for Text and Language Processing.

\item {Koby Crammer}, Eyal Even-Dar, Yishay Mansour and Jennifer Wortman.
\href{}{Regret Minimization with Concept Drift}. 3rd Annual Machine Learning Symposium, 2008
\item
Kedar Bellare, {Koby Crammer } and Dayne Freitag .
\href{http://www.cis.upenn.edu/~crammer/publications/miraed_09.pdf}{Loss-Sensitive Discriminative Training of Machine Transliteration Models}. NAACL Student Research Workshop poster, 2009.

% \item Mark Dredze, Partha Pratim Talukdar and {K___oby Crammer}.
\href{http://webee.technion.ac.il/people/koby/publications/mld09_multi_label.pdf}{Sequence Learning from Data with Multiple Labels}.
ECML-PKDD 2009 workshop on Learning from Multi-Label Data (MLD), 2009
\item
\href{http://webee.technion.ac.il/publication-link/index/id/596/abstract/1}{Confidence Estimation in Structured Prediction}.
Avihai Mejer and {Koby Crammer}.
CCIT Report 798, 2011.

\item
\href{webee.technion.ac.il/publication-link/index/id/641}{Sequential Voice Conversion Using Grid-Based Approximation}.
Hadas Benisty, David Malah, and {Koby Crammer}.
CCIT Report 843, 2013.
\end{enumerate}

\end{document}
